A pipeline to analyse time-course gene expression data

### 2020-07-16 scripts/manuscript.Rmd
changes
update manuscript
fix error in manuscript

```{r genesVsCentroids, fig.height=6, fig.width=6}
cluster_of_interest = 2
cluster2Genes = names(
    kmeans_clusters$clusters[kmeans_clusters$clusters==cluster_of_interest])
dataToPlot=rbind(assay(de_moanin_model[cluster2Genes[3:6],]), 
    "Centroid"=kmeans_clusters$centroids[cluster_of_interest,])
plot_splines_data(de_moanin_model,  data=dataToPlot, 
    colors=ann_colors$Group, smooth=TRUE,simpleY =FALSE,
    mar=c(1.5,2.5,2,0.1))
```

@@

```{r}
de_moanin_rescale = de_moanin_model
assay(de_moanin_rescale) = rescale_values(data=assay(de_moanin_model))
plot_splines_data(de_moanin_rescale,  data=kmeans_clusters$centroids[cluster_of_interest,], 
    colors=ann_colors$Group, smooth=TRUE,simpleY =FALSE,
    data_smooth_only=TRUE, subset_data=cluster2Genes[3:6],
    mar=c(1.5,2.5,2,0.1))
```
**EAP** I added the functionality to plot centroid over data, rather than just fit to data, but I'm not sure it makes much sense to include this. The `rescale_values` function is too sensitive to outliers. Would be better to rescale each centroid to scale of gene. If we had a helper function to do that, could easily add that to plot_splines_data (made issue on moanin), but probably right now should remove this.

@@

kmeans_clusters = splines_kmeans(de_moanin_model[indices,],
    n_clusters=n_clusters,
    random_seed=random_seed,
    n_init=20)

@@

# Competing interests
The authors declare that they have no competing interests.

>>>>

```{r genesVsCentroids, fig.height=6, fig.width=6}
cluster_of_interest = 2
cluster2Genes = names(
    kmeans_clusters$clusters[kmeans_clusters$clusters==cluster_of_interest])
dataToPlot=rbind(as.matrix(assay(de_moanin_model[cluster2Genes[3:6],])), 
    "Centroid"=kmeans_clusters$centroids[cluster_of_interest,])
plot_splines_data(de_moanin_model,  data=dataToPlot, 
    colors=ann_colors$Group, smooth=TRUE,simpleY =FALSE,
    mar=c(1.5,2.5,2,0.1))
```

@@

```{r}
de_moanin_rescale = de_moanin_model
assay(de_moanin_rescale) = rescale_values(data=assay(de_moanin_model))
plot_splines_data(de_moanin_rescale,  
    centroid=kmeans_clusters$centroids[cluster_of_interest,], 
    colors=ann_colors$Group, smooth=TRUE,simpleY =FALSE,
    subset_data=cluster2Genes[3:6],
    mar=c(1.5,2.5,2,0.1))
```
**EAP** I added the functionality to plot centroid over data, rather than just fit to data, but I'm not sure it makes much sense to include this. The `rescale_values` function is too sensitive to outliers. Would be better to rescale each centroid to scale of gene. If we had a helper function to do that, could easily add that to plot_splines_data (made issue on moanin), but probably right now should remove this.

@@

kmeans_clusters = splines_kmeans(de_moanin_model[indices,],
    n_clusters=n_clusters,
    random_seed=42,
    n_init=20)

@@

# Competing interests

The authors declare that they have no competing interests.
